The Bug Catalog of the Maven Ecosystem

### 2014-02-20 docs/msr.tex
added data collection

The whole process produced a file list with all the valid {\sc jar} files for our experinment.

>>>>

The whole process produced a file list with all the valid {\sc jar} files for our experinment. Each file on the list were uploaded as a separate task in the task queue (Figure~XXX). Concurent workers processed each task and submitted the results to the mongo database.

When the processing was completed, we ran a series of sanity checks on the results, to check their validity. We discovered several issues, which we addressed with various approaches. The most common problem was Findbugs out-of-memory crashes, which demanded to repeat the process for those {\sc jar}s with the appropriate settings in the Java runtime environment.

The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct.
